Compiling refinement types to dependent types

### 2020-07-15 tex/paper.tex
Start working on the bibliography
We probably won't have ADT/PM in our core language
Build fix
Add references for ADT/PM for the surface language

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}
\usepackage{cite}
\usepackage{amsthm}

@@

Our surface language is based on simply typed lambda calculus.
Refinements over the types are, of course, the most important extension.
The other ones are:
\begin{itemize}
  \item dependent arrow types, to allow subsequent refinements refer preceding arguments,
  \item limited form of algebraic data types and dependent pattern matching,
    to illustrate reasoning about those widely used constructs.
\end{itemize}

@@

We take $\lambda C$ \cite{Nederpelt14}
enriched with case-splitting inspired by \cite{TAPLVariants,EisenbergThesis}
and a unit type as our core dependently typed language.

@@

>>>>

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}
\usepackage{cite}
\usepackage{url}
\usepackage{babelbib}
\usepackage[english]{babel}
\usepackage{amsthm}

@@

Our surface language is based on simply typed lambda calculus.
Refinements over the types are, of course, the most important extension.
The other ones are:
\begin{itemize}
  \item dependent arrow types, to allow subsequent refinements refer preceding arguments,
  \item limited form of algebraic data types and dependent pattern matching
    insired by \cite{TAPLVariants,Eisenberg16},
    to illustrate reasoning about those widely used constructs.
\end{itemize}

@@

We take $\lambda C$ \cite{TTFPLambdaC}
with a unit type as our core dependently typed language.

@@

\bibliographystyle{babunsrt-lf}
\bibliography{biblio}
